\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Nadeem Ali} % Your name
% You can merge both of these into a single line, if you do not have a website.
\address{+91-9045667996 \\ Noida, India}
\address{\href{mailto:nadeemali001@gmail.com}{nadeemali001@gmail.com} \\ \href{https://linkedin.com/in/nadeemali001}{linkedin.com/in/nadeemali001} \\ \href{www.nadeemali.top}{www.nadeemali.top}}  %

\begin{document}
\begin{sloppypar}

%----------------------------------------------------------------------------------------
%	OBJECTIVE
%----------------------------------------------------------------------------------------

    \begin{rSection}{Summary}

    {L2 Trading Support | Dev-Ops and AWS |Automation Expert | Python/Shell Scripting/SQL | ITIL Foundation Certified ITRS Geneos Specialist}


    \end{rSection}
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

    \begin{rSection}{Education}

    {\bf Bachelor of Technology}, Dr. A.P.J. Abdul Kalam Technical University \hfill {Aug 2010 - Jun 2014}\\
    Relevant Coursework: Computer Science and Engineering
    \end{rSection}

%----------------------------------------------------------------------------------------
% TECHINICAL STRENGTHS
%----------------------------------------------------------------------------------------
\begin{rSection}{SKILLS}
    \begin{tabular}{ l | l }
    Technical Skills &  AWS, DevOps, Python,Shell Scripting, SQL \\
    Soft Skills & Automation, Autosys, Control-M, ITRS-Geneos,Infrastructure as code (IaaC)\\
    Functional Skills & Trading Support, Exchange (FX) Trading, Equity Derivates, Amazon Seller Support\\
    \end{tabular}\\
    \end{rSection}

    \begin{rSection}{EXPERIENCE}

        \textbf{Technical Specialist} \hfill Jan 2023 - Present\\
        Fidelity International \hfill \textit{Gurgaon, IN}
        \begin{itemize}
            \itemsep -3pt {}
            \item Proficient in analysing, managing and integrating Charles River Trading platform, OMS and FIX Protocol.
            \item Strong project management skills, leading complex Trading system implementation projects on time and within budget and providing technical support.
            \item Effective communication with traders, portfolio managers, and stakeholders within Trading environment to align system solutions with business objectives.
        \end{itemize}

        \textbf{Support Engineer III (DevOps Engineer)} \hfill Mar 2022 - Jan 2023\\
        Amazon India \hfill \textit{Bangalore, IN}
        \begin{itemize}
            \itemsep -3pt {}
            \item Upgrade system and apps for latest patches using CI/CD pipelines.
            \item Work on AWS account for various services (IAM, CloudWatch, DynamoDB to name a few).
            \item Work on multiple issues which needs debug and root cause findings. Also, deploy fixes using Jenkins.
            \item Work on automations to auto-heal tickets coming from sellers.
        \end{itemize}

        \textbf{Senior Analyst Programmer} \hfill Feb 2018 - Mar 2022\\
        Fidelity International \hfill \textit{Noida, IN}
        \begin{itemize}
            \itemsep -3pt {}
            \item Worked in Research System as L2 support and helped analysts to write the research effortlessly on supporting apps.
            \item Develop, analyse, and refine programs, incorporating workflow charts and client feedback.
            \item Provide cost advice and design recommendations while testing software patches.
            \item Worked on initial discussion around migration of in-house applications to Cloud (AWS) and adoption of Dev-Ops.
        \end{itemize}

        \textbf{Software Engineer} \hfill Dec 2014 - Jan 2018\\
        Deutsche Bank \hfill \textit{Pune, IN}
        \begin{itemize}
            \itemsep -3pt {}
            \item Collaborated with engineers or software developers to select appropriate design solutions or ensure the compatibility of system components.
            \item Evaluated current or emerging technologies to consider factors such as cost, portability, compatibility, or usability.
            \item Provided technical guidance or support for the development or troubleshooting of systems.
        \end{itemize}

    \end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

    \begin{rSection}{PROJECTS}
        \vspace{-1.25em}
        \item \textbf{Charles River Development Trading.} {Worked on an Trading platform and help traders to book the trades and provide support to them in case of any issues. \href{https://www.crd.com/company/about-us/}{(Try it here)}}
        \item \textbf{Amazon Seller Support.} {Helped sellers to get onboard on the platform and resolves queries while registering. \href{https://sell.amazon.com/}{(Try it here)}}
        \item \textbf{Research Management System.} {FIL Internal application which is used to help analysts to write research on companies which can help portfolio manager to take buy and sell decision effeciently.}
        \item \textbf{Imagine DB} {Supported Deutsche Bank internal tools to help trading to book equity trades and register PnL reports.}
    \end{rSection}

%----------------------------------------------------------------------------------------
    \begin{rSection}{Extra-Curricular Activities}
        \begin{itemize}
            \item 	Actively working on sharping my skills.
            \item  	Actively working on AWS/Dev-Ops GIT projects.
        \end{itemize}


    \end{rSection}

%----------------------------------------------------------------------------------------

\end{sloppypar}
\end{document}